# Part 3

```{r}
library(satchel)
```

```{r}
satchel <- Satchel$new("part3", "../data/derived/satchel")
```

```{r}
# see whats available
satchel$available()
```

If I want to use sd_oral_richpk, I can still reference it directly as it was only created in Part1

```{r}
pkdat <- satchel$use("sd_oral_richpk")
head(pkdat)
```

However, an object named `Theoph` was saved in both Part1 and part 2

```{r, eval = F}
satchel$use("Theoph")
```

```
Error in satchel$use("Theoph") : multiple matches found, please specify where the data was specified as well
```

so we must specify what namespace it was saved in explicitly

```{r}
theoph <- satchel$use("Theoph", "part1")
head(Theoph)
```

If the dataset was large and I didn't want to load it completely, I could also check it quickly with preview, which will pull from a separate metadata cache satchel keeps track of, so the entire object does not have to be loaded. This can be significant in memory/time savings when dealing with large objects.

```{r}
satchel$preview("Theoph", "part1")
```


```{r}
devtools::session_info()
```


